Suplementary Material 3: Run Simulations on the Last Birth Omited Data

### 2023-04-04 S3_run_simulations_EE_not_last.Rmd
run only failed parts

```{r fit models}
## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
  fits <- fit_life_histories(scenario = scenario,
                             birth_level_data = data_births_monthly)
  save(fits, file = paste0(fitDir,"/fits_", scenario, "_obs.rda"), compress = "xz")

  rm(fits)
  }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)
```

@@

   slopes_under_scenario <- simulate_slopes_for_GOF(N_replicates_level1 = 200L,
                                                    N_replicates_level2 = 49L,
                                                    birth_level_data = data_births_monthly,
                                                    life_history_fits = fits,
                                                    scenario = scenario,
                                                    nb_cores = nb_cores,
                                                    timeout = timeout,
                                                    .log = TRUE, lapply_pkg = "pbmcapply",
                                                    verbose = list(fit = TRUE, simu = FALSE))
   rm(fits)
   name_obj <- paste0("slopes_under_", scenario)
   assign(name_obj, value = slopes_under_scenario)
   save(list = name_obj, file = paste0(slopeDir,"/", name_obj, ".rda"))
   rm(list = name_obj) # remove the object behind the name!
   rm(slopes_under_scenario, scenario, name_obj) # remove the object directly
   gc_stuff <- gc(verbose = FALSE)
}
```

>>>>

```{r fit models}
## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
  targetFname <-  paste0(fitDir,"/fits_", scenario, "_obs.rda")
  if(!file.exists(targetFname)){
    fits <- fit_life_histories(scenario = scenario,
                             birth_level_data = data_births_monthly)
    save(fits, file =targetFname, compress = "xz")

    rm(fits)
  }

  }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)
```

@@

   name_obj <- paste0("slopes_under_", scenario)
   targetFname <- paste0(slopeDir,"/", name_obj, ".rda")
   if(!file.exists(targetFname)){
     slopes_under_scenario <- simulate_slopes_for_GOF(N_replicates_level1 = 200L,
                                                      N_replicates_level2 = 49L,
                                                     birth_level_data = data_births_monthly,
                                                      life_history_fits = fits,
                                                      scenario = scenario,
                                                      nb_cores = nb_cores,
                                                      timeout = timeout,
                                                      .log = TRUE, lapply_pkg = "pbmcapply",
                                                      verbose = list(fit = TRUE, simu = FALSE))
     rm(fits)
     assign(name_obj, value = slopes_under_scenario)
     save(list = name_obj, file = targetFname)
     rm(list = name_obj) # remove the object behind the name!
     rm(slopes_under_scenario, scenario, name_obj) # remove the object directly
     gc_stuff <- gc(verbose = FALSE)
   }

}
```

### 2023-04-04 S3_run_simulations_original_not_last.Rmd
run only failed parts

```{r fit models}
## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
  fits <- fit_life_histories(scenario = scenario,
                             birth_level_data = data_births_monthly)
  save(fits, file = paste0(fitDir,"/fits_", scenario, "_obs.rda"), compress = "xz")

  rm(fits)
  }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)
```

>>>>

```{r fit models}
## fit all trios of models in parallel (for linux only, but easy to adjust for other OS):
pbmcapply::pbmclapply(scenarios_to_do, function(scenario) {
  targetFname <-  paste0(fitDir,"/fits_", scenario, "_obs.rda")
  if(!file.exists(targetFname)){
    fits <- fit_life_histories(scenario = scenario,
                               birth_level_data = data_births_monthly)
    save(fits, file = targetFname, compress = "xz")

    rm(fits)
  }
  }, mc.cores = min(c(length(scenarios_to_do), nb_cores)), mc.preschedule = FALSE)
```
